---
title: "Stats 1 - Lab 7"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


# Normal distribution

+ To calculate $F(x) = \Pr(X \le x)$ (CDF) where $X \sim \mathcal{N}(\mu, \sigma^2)$ we can use the function `pnorm(x, mean, sd)` where `x` is the outcome $x,$ `mean` is $\mu$, and `sd` is the **standard deviation** $\sigma.$

+ To calculate quantiles $x$ such that $\Pr(X \le x) < p$ (CDF) where $X \sim \mathcal{N}(\mu, \sigma^2)$ we can use the function `qnorm(p, mean, sd)` where `p` is $p,$ `mean` is $\mu$, and `sd` is the **standard deviation** $\sigma.$

## Task

+ Suppose $X$ is a standard Normal distribution. Find $\Pr(-0.1 < X < 0.2).$
```{r normal_1, exercise = TRUE}

```
**Solution:** `r pnorm(0.2) - pnorm(-0.1)`

+ Suppose $X \sim \mathcal{N}(\mu = -3, \sigma^2 = 5.7).$ Find $\Pr(X < -2 \mid X < -1.3).$
```{r normal_2, exercise = TRUE}

```
**Solution:** `r pnorm(-2, -3, sqrt(5.7)) / pnorm(-1.3, -3, sqrt(5.7))`

+ Suppose $X \sim \mathcal{N}(\mu = 0.5, \sigma^2 = 9.2).$ Find $x_1$ and $x_2$ such that $\Pr(X < x_1) = 0.13$ and $\Pr(X > x_2) = 0.17.$
```{r normal_3, exercise = TRUE}

```
**Solution: $x_1 = `r x1 <- qnorm(0.13, 0.5, sqrt(9.2)); x1`,$** **$x_2 = `r x2 <- qnorm(1 - 0.17, 0.5, sqrt(9.2)); x2`$**
