---
html_document:
  mathjax: http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML
output:
  html_document:
    code_folding: show
    number_sections: false
title: "Computing probabilities using R"
---
<style type="text/css">
body {
font-size: 17px;
}
.tabbed-pane { 
border-style: solid;
border-top-style: none;
border-width: 1px;
border-color: #e2e2e2; 
padding: 10px;
}
.section h1 {
padding-top: 100px;
font-size: 41px;
}
.section h2 {
padding-top: 120px;
}
.section h3 {
padding-top: 90px;
}
.section h4 {
padding-top: 90px;
}
</style>

<script src="//yihui.name/js/math-code.js"></script>
<!-- Just one possible MathJax CDN below. You may use others. -->
<script async
  src="//mathjax.rstudio.com/latest/MathJax.js?config=TeX-MML-AM_CHTML">
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, cache = FALSE)
```

____

R can compute a variety of probabilities for many families of discrete and continuous distributions (Binomial, Poisson, Normal, etc.)

- `dfamily(x = x, parameters)` computes the **PMF** for discrete r.v.s or **PDF** for continuous r.v.s of family evaluated at $x$.

- `pfamily(q = x, parameters)` computes the **CDF** of family evaluated at $x$.

### Examples

+ Suppose $X \sim Geometric(p = 0.3).$ Let's find $\Pr(X = 4) = p(4).$
```{r}
dgeom(4, 0.3)
```

+ Suppose $X \sim Binomial(n = 7, p = 0.8).$ Let's find $\Pr(X \le 5) = F(5).$
```{r}
pbinom(5, 7, 0.8)
```

+ Suppose $X \sim \mathcal{N}(\mu = 23, \sigma^2 = 14).$ Let's find $\Pr(20 < X \le 22) = F(22) - F(20).$
```{r}
pnorm(22, 23, sqrt(14)) - pnorm(20, 23, sqrt(14))
```

+ If $X$ is a random variable which does not belong to any fistribution family but it's defined by a PDF like, for example, $f(x) = \dfrac{3}{8}(4x − 2x^2),\ 0 < x < 2.$ We can find probabilities like, for example, $\Pr(0.8 < X < 1.4)$ using the `intergrate()` function.
```{r}
f <- function(x) 3 / (8 * (4 * x - 2 * (x^2)))
integrate(f, 0.8, 1.4)$value
```

#### <a href="https://acaimo.shinyapps.io/R_lab/" target="_blank">R lab tutorial</a>
