---
title: "Statistics 1 - Lab 5"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


### Discrete random variables

+ To calculate $p(x) = \Pr(X = x)$ (PMF) where $X \sim Geometric(p)$ we can use the function `dgeom(x, prob)` where `x` is the outcome $x$ and `prob` is the probability of success $p.$ 

+ To calculate $F(x) = \Pr(X \le x)$ (CDF) where $X \sim Geometric(p)$ we can use the function `pgeom(x, prob)` where `x` is the outcome $x$ and `prob` is the probability of success $p.$ 

For example, suppose that $X \sim Geometric(p = 0.32)$ and we want to calculate $\Pr(X > 4):$
```{r, eval = TRUE, echo = TRUE}
1 - pgeom(4, 0.32)
```

+ The R functions for the PMF and CDF of $X \sim Binomial(n, p)$ are `dbimom(x, size, prob)` and `pbimom(x, size, prob)` respectively, where `size` is the number of trials `n`.

+ The R functions for the PMF and CDF of $X \sim Poisson(\lambda)$ are `dpois(x, lambda)` and `pbimom(x, lambda)` respectively, where `lambda` is the rate parameter

## Task

1. Suppose $X \sim Binomial(n = 10, p = 0.2).$ Find $\Pr(X = 3 \mid X < 6).$
```{r binomial, exercise = TRUE}

```
**Solution: `r dbinom(3, 10, 0.2) / pbinom(5, 10, 0.2)`**

2. Suppose $X \sim Poisson(\lambda = 8).$ Find $\Pr(X < 4 \cup X > 9).$
```{r poisson, exercise = TRUE}

```
**Solution: `r ppois(3, 8) + ppois(9, 8, lower.tail = FALSE)`**
